Programming Future Parallel Architectures\\ with Haskell and Intel ArBB

### 2013-11-13 src2/arbb/paperThesis.tex
updated writing
update

Our first \systemname{} prototype adapts an existing EDSL called {\em
  Accelerate} (Data.Array.Accelerate).  Accelerate targets high-level
data-parallel programming in Haskell.
Previous work on Accelerate has focused on developing a CUDA-backend
for GPU programming.  In this paper we describe our effort to retarget
Accelerate to ArBB.

@@

Microsoft Accelerator~\citearbb{ACCELERATOR} is an embedded language with similar 
aspirations as ArBB, that is, to target a diverse range of architectures using the 
same source code. Accelerate can be used from the C\# language or the 
functional F\# language and targets GPUs or of CPUs and their
vector units.
% However, being part of the .Net framework implies limited accessibility 
%for platforms other than Microsoft Windows.

@@

%{
%\small
\bibliographystylearbb{alpha}
\bibliographyarbb{thesis}
%}

>>>>

Our first \systemname{} prototype adapts an existing EDSL called {\em
  Accelerate}.  Accelerate targets high-level
data-parallel programming in Haskell.
Previous work on Accelerate has focused on developing a CUDA-backend
for GPU programming.  In this paper we describe our effort to retarget
Accelerate to ArBB.

@@

Microsoft Accelerator~\citearbb{ACCELERATOR} is an embedded language with similar 
aspirations as ArBB, that is, to target a diverse range of architectures using the 
same source code. Accelerator can be used from the C\# language or the 
functional F\# language and targets GPUs or of CPUs and their
vector units.
% However, being part of the .Net framework implies limited accessibility 
%for platforms other than Microsoft Windows.

@@

%{
%\small
\bibliographystylearbb{alpha}
\bibliographyarbb{thesis}
\addcontentsline{toc}{subsection}{Bibliography}
%}
